The \dealii{} Library, Version 8.5

### 2017-03-16 8.5/paper.tex
add a blurb about tutorials

\subsection{The physics module}

@@

>>>>

\subsection{The physics module}
\label{sec:physics}

@@

\subsection{New and updated tutorial programs}

\begin{itemize}
 \item {\bf step-55} is a new tutorial that explains how to solve the Stokes 
 equations efficiently in parallel. It is a good introduction to solving
 systems of PDEs in parallel, discusses optimal block 
 preconditioners, and demonstrates other aspects like error computation.
 Inverses of individual blocks of the linear system are approximated with an algebraic 
 multigrid preconditioner.

 \item {\bf step-56} is a new tutorial that shows how to apply geometric multigrid
 preconditioners on a subset of a system of PDEs. The problem solved here is the 
 Stokes equations, like in step-55.

 \item {\bf step-57} is a new tutorial that solves the stationary Navier-Stokes equations.
 The nonlinear system is solved using Newton's method on a sequence of adaptively refined
 grids. The preconditioner is again built on a block factorization of the saddle point
 system like in step-55 and step-56, but the non-symmetric terms stemming from the
 nonlinear convective part requires more sophisticated solvers. The benchmark problem,
 flow in the 2d lid-driven cavity, requires a continuation method for high Reynold's 
 numbers.

 \item {\bf step-37}, discussing matrix-free computations of the 
 Poisson equation, has been rewritten to support parallel computations.

 \item {\bf step-44} now uses the physics module, discussed in Section~\ref{sec:physics},
 to solve a solid mechanics problem.
 \end{itemize}
